---
title: "R Introduction; data structure, data import and ouput"
output: html_notebook
---
#Problem 1--------------------------------------------------------------
```{r}
#install R:
```
open an internet browser (in this part i choosed 'chrome') and go to Google.com
type the words "download r" in the search engine (Google.com)
click "Download R-3.5.1 for Windows. The R-project for statistical computing"
click "Download R 3.5.1 for Windows"
save on our computer, run the file and follow the installation instructions
now R is installed
```{r}
#install Rstudio:
```
open an internet browser (in this part i choosed 'chrome') and go to *Google.com*
type the words "download latest version of rstudio for windows" in the search engine (Google.com)
click "Download Rstudio-Rstudio"
click "Product" then click "download rstudio dekstop"
click the latest windows version and save file to our computer, run the file and follow the installation instructions
```{r}
#install basic R packages:
```
install Rnotebook:
click "file" -> "new file" -> "R Notebook"
install quantmod:
open RStudio
install.packages("quantmod")

#Problem 2--------------------------------------------------------------
```{r}
#STEP 1 Install or Load "quantmod" package
#Get quantmod
if (!require("quantmod")) {
  install.packages("quantmod")
  library(quantmod)
}
```
```{r}
#Let's get Apple stock data; Apple's ticker symbol is AAPL. We use the
#quantmod function getSymbols, and pass a string as a first argument to
#identify the desired ticker symbol, pass 'yahoo' to src for Yahoo!
#Finance, and from and to specify date ranges
```
```{r}
#The default behavior for getSymbols is to load data directly into the
#global environment, with the object being named after the loaded ticker
#symbol. This feature may become deprecated in the future, but we exploit
#it now.
```
```{r}
#STEP 2 Grab online "AAPL" dataset by using getSymbols()
getSymbols("AAPL", src = "yahoo")
```
```{r}
#STEP 2 Convert to dataframe
load("C:/Users/sitti khadijah/Documents/homework1/AAPLkdj.Rda")
df <- data.frame(Date=index(AAPL),coredata(AAPL))
```
```{r}
#STEP 3 SAVE "AAPL" dataset to directory
save(df,file="C:/Users/sitti khadijah/Documents/homework1/AAPLkdj.Rmd")
```
```{r}
#STEP 4 Pick the value more than 200 select by AAPL.Open
DF <- df[df$AAPL.Open>200,]
```
```{r}
#STEP 5 Descending
DF <- DF[with(DF, order(-DF$AAPL.Open)), ]
```
```{r}
#STEP 6 Sort 1-10
DF <- DF[order(1:10),]
```
```{r}
#STEP 7 SAVE "RESULTS" to directory
save(DF,file="C:/Users/sitti khadijah/Documents/homework1/AAPLkdj.Rmd")
```
```{r}
print(DF)
```
#Problem 3--------------------------------------------------------------
```{r}
#STEP 1  attach the iris dataset to the environment
data(iris)
```
```{r}
# STEP 2 rename the dataset
dt <- iris
```
```{r}
# STEP 3 make a function for search and replace
kdj <- function(Source, Search, Replace)
{
  if (length(Search) != length(Replace))
    stop("Search and Replace Must Have Equal Number of Items\n")
  
  Changed <- as.character(Source)
  
  for (i in 1:length(Search))
  {
    cat("Replacing: ", Search[i], " With: ", Replace[i], "\n")
    Changed <- replace(Changed, Changed == Search[i], Replace[i])
  }
  
  cat("\n")
  
  Changed
}
```
```{r}
# STEP 4 Do search and replacement levels of ('setosa', 'versicolor', 'virginica') into three numbers(1, 2, 3).
dt$Species <- as.numeric(kdj(dt$Species, 
                             c("setosa", "versicolor", "virginica"), 
                             c(1, 2, 3)))
```
```{r}
# STEP 5 Summarize Dataset after replacement, with following
```
```{r}
#1 Dimensions of the dataset.
print(dim(dt))
```
```{r}
#2 Types of the attributes.
sapply(dt, class)
```
```{r}
#3 Peek at the data itself.
head(dt)
```
```{r}
#4 Levels of the class attribute.
levels(dt$Species)
```
```{r}
#5 Breakdown of the instances in each class.
percentage <- prop.table(table(dt$Species)) * 100
cbind(freq=table(dt$Species), percentage=percentage)
```
```{r}
#6 Statistical summary of all attributes.
summary(dt)
```
```{r}
# STEP 6 Visualize Dataset corresponding to Species variable after replacement
# split input and output
x <- dt[,1:4]
y <- dt[,5]

# boxplot for each attribute on one image
par(mfrow=c(1,4))
for(i in 1:4) {
  boxplot(x[,i], main=names(iris)[i])
}
```